HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-19 paper/main.tex
repository

@@

\section*{Acknowledgments}
{T}his work was conducted within the scope of the \ProjectType, which has received funding from the European Union's Horizon 2020 research and innovation programme under grant agreement No \GrantNo (\ProjectName).

>>>>

All annotation data gathered in this project, together with analysis scripts is available
in github\footnote{\url{https://github.com/bhaddow/hume-emnlp16}}.

@@

\section*{Acknowledgments}
{T}his work was conducted within the scope of the \ProjectType, which has received funding from the European Union's Horizon 2020 research and innovation programme under grant agreement No \GrantNo\ (\ProjectName).
